Precise predictions for same-sign W-boson scattering at the LHC

### 2018-03-12 Draft/article.tex
Fix typos

    The first observation is that the predictions featuring two versions
    of the VBS approximation ({\sc Bonsay} and the {\sc Powheg-Box}) are
    relatively close.\footnote{The {\sc VBFNLO}-predictions omitting
    $s$-channel contributions amounts to $1.3703(1)$ fb. This differs from
    the {\sc Powheg-Box} prediction mainly due to the different choice of
    scales used in the {\sc Powheg-Box} (\emph{cf.}
    footnote \ref{foot:powheg}).} {\sc Bonsay} uses a double-pole
    approximation for the virtual matrix element, and it is worth noticing
    that this approximation seems to be accurate at $1\%$ level as
    compared to the {\sc Powheg-Box}. This means that the double-pole
    approximation on the two W bosons used in {\sc Bonsay} constitutes a
    good approximation of the VBS-approxi\-mated virtual corrections
    implemented in the {\sc Powheg-Box}.  Both predictions differ by about
    $2\%$ with respect to the full computation ({\sc MoCaNLO+Recola}).
    The second observation is that the inclusion of $s$-channel
    contributions seems to have a significant impact.  Indeed, their
    inclusion (as done in {\sc VBFNLO}) approximates the full computation
    by less than a per cent ($0.7\%$). The main contribution due to 
    the $s$-channel diagrams thereby consists of real-emission
    contributions, where one of the two leading jets is formed by one
    quark, or possibly also both quarks, originating from the W-boson decay,
    and the second one by the extra radiation emitted from the initial
    state. In such configurations, the hadronically-decaying W boson can
    become on-shell and hence yield larger contributions than at LO, where
    the invariant mass cut on the two jets forces the boson into the far
    off-shell region.
    However, the agreement between {\sc MoCaNLO+Recola} and {\sc VBFNLO} is mostly accidental, as the inclusion of interference effect and some non-factorisable corrections (in the real corrections) in {\sc MG5\_aMC} brings the prediction down and closer to the VBS approximation.
    Not unexpectedly none of the approximations used here agree perfectly with the full calculation of {\sc MoCaNLO\-+Recola} at NLO.
    Nevertheless, the disagreement seems to never exceed $2\%$ at the fiducial cross section level.

@@

Finally, focusing on the third jet, we conclude the list of differential observables by showing the Zeppenfeld variable defined in Eq.~\eqref{eq:Zeppenfeld}, Fig.~\ref{fig:PSz3}. This
variable is closely related to the third jet rapidity, and small (large) values of $z$ correspond to central (peripheral) rapidities. In general, for observables which involve the third jet, one
can clearly see a degradation of the agreement among the various tools, because of the poorer perturbative description of these observables. The Zeppenfeld variable is
a striking example: both at LO and NLO, the tendency of {\sc Pythia8} to generate more hard and central radiation, corresponding to low values of $z$,
is clearly visible. Such an effect, which is related to the way {\sc Pythia8} deals with the recoil of the radiation in VBF(VBS)-type processes,
can be mitigated by setting {\tt SpaceShower:dipole\-Recoil = on} in the {\sc Pythia8} input file.\footnote{This requires version $\ge8.230$.
Note that such a setting is not compatible with the NLO matching
in {\sc MG5\_aMC} (but it is compatible with the {\sc Powheg} matching). Also, this setting has other
effects, though smaller, on the rapidity spectra of the two hardest jets.} It is interesting to notice that
the effect survives beyond the first emission, as it can be observed by comparing {\sc Powheg-LHE} with {\sc Powheg+ Pythia8}. A similar
behaviour of {\sc Pythia8}
has also been observed in the study of EW production of a $\PZ$ boson in association with two jets (see the recent CMS measurement,
Ref.~\cite{Sirunyan:2017jej} Figure 12), where the experimental data seem to prefer the description by {\sc Herwig++}.
The central enhancement
is a bit mitigated if NLO+PS tools are used (compare LO+PS and NLO+PS from {\sc MG5\_aMC+Pythia8} with the fixed-NLO prediction), however even at NLO+PS the central region
($z_{j_3}<0.5$) is cursed by huge differences between tools. Large differences, reaching a factor 2, persist also away from the central region. These findings are consistent with behaviour displayed in Refs.~\cite{Jager:2011ms,Jager:2012xk,Jager:2013mu,Jager:2013iza,Schissler:2013nga} where the behaviour of NLO mathcing in VBS processes have been reported.\\

>>>>

    The first observation is that the predictions featuring two versions
    of the VBS approximation ({\sc Bonsay} and the {\sc Powheg-Box}) are
    relatively close.\footnote{The {\sc VBFNLO} prediction omitting
    $s$-channel contributions amounts to $1.3703 \pm 0.0001$ fb. This differs from
    the {\sc Powheg-Box} prediction mainly due to the different choice of
    scales used in the {\sc Powheg-Box} (\emph{cf.}
    footnote \ref{foot:powheg}).} {\sc Bonsay} uses a double-pole
    approximation for the virtual matrix element, and it is worth noticing
    that this approximation seems to be accurate at $1\%$ level as
    compared to the {\sc Powheg-Box}. This means that the double-pole
    approximation on the two W bosons used in {\sc Bonsay} constitutes a
    good approximation of the VBS-approxi\-mated virtual corrections
    implemented in the {\sc Powheg-Box}.  Both predictions differ by about
    $2\%$ with respect to the full computation ({\sc MoCaNLO+Recola}).
    The second observation is that the inclusion of $s$-channel
    contributions seems to have a significant impact.  Indeed, their
    inclusion (as done in {\sc VBFNLO}) approximates the full computation
    by less than a per cent ($0.7\%$). The main contribution due to 
    the $s$-channel diagrams thereby consists of real-emission
    contributions, where one of the two leading jets is formed by one
    quark, or possibly also both quarks, originating from the W-boson decay,
    and the second one by the extra radiation emitted from the initial
    state. In such configurations, the hadronically-decaying W boson can
    become on-shell and hence yield larger contributions than at LO, where
    the invariant mass cut on the two jets forces the boson into the far
    off-shell region.
    However, the agreement between {\sc MoCaNLO+Recola} and {\sc VBFNLO} is mostly accidental, as the inclusion of interference effect and some non-factorisable corrections (in the real corrections) in {\sc MG5\_aMC} brings the prediction down and closer to the VBS approximation.
    Not unexpectedly none of the approximations used here agree perfectly with the full calculation of {\sc MoCaNLO\-+Recola} at NLO.
    Nevertheless, the disagreement seems to never exceed $2\%$ at the fiducial cross section level.

@@

Finally, focusing on the third jet, we conclude the list of differential observables by showing the Zeppenfeld variable defined in Eq.~\eqref{eq:Zeppenfeld}, Fig.~\ref{fig:PSz3}. This
variable is closely related to the third jet rapidity, and small (large) values of $z$ correspond to central (peripheral) rapidities. In general, for observables which involve the third jet, one
can clearly see a degradation of the agreement among the various tools, because of the poorer perturbative description of these observables. The Zeppenfeld variable is
a striking example: both at LO and NLO, the tendency of {\sc Pythia8} to generate more hard and central radiation, corresponding to low values of $z$,
is clearly visible. Such an effect, which is related to the way {\sc Pythia8} deals with the recoil of the radiation in VBF(VBS)-type processes,
can be mitigated by setting {\tt SpaceShower:dipole\-Recoil = on} in the {\sc Pythia8} input file.\footnote{This requires version $\ge8.230$.
Note that such a setting is not compatible with the NLO matching
in {\sc MG5\_aMC} (but it is compatible with the {\sc Powheg} matching). Also, this setting has other
effects, though smaller, on the rapidity spectra of the two hardest jets.} It is interesting to notice that
the effect survives beyond the first emission, as it can be observed by comparing {\sc Powheg-LHE} with {\sc Powheg+ Pythia8}. A similar
behaviour of {\sc Pythia8}
has also been observed in the study of EW production of a $\PZ$ boson in association with two jets (see the recent CMS measurement,
Ref.~\cite{Sirunyan:2017jej} Figure 12), where the experimental data seem to prefer the description by {\sc Herwig++}.
The central enhancement
is a bit mitigated if NLO+PS tools are used (compare LO+PS and NLO+PS from {\sc MG5\_aMC+Pythia8} with the fixed-NLO prediction), however even at NLO+PS the central region
($z_{j_3}<0.5$) is cursed by huge differences between tools. Large differences, reaching a factor 2, persist also away from the central region. These findings are consistent with behaviour displayed in Refs.~\cite{Jager:2011ms,Jager:2012xk,Jager:2013mu,Jager:2013iza,Schissler:2013nga} where the behaviour of NLO matching in VBS processes has been reported.\\
